---
title: "Nudge Data"
author: "Sydney Sorkin"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(readr)
library(fs)
library(infer)
library(janitor)
library(tidyverse)
```

```{r data cleaning}
dir.create("raw_data")
survey_data <- read_csv("raw_data/Athlete_Survey_11-09-2019.csv") %>% 
  clean_names() 

#rows 1 and 2 from imported data are duplicate rows

cleaned_survey <- survey_data[-c(1,2), ] %>% 
  select(finished, q5, q8, q10) %>% 
  filter(finished == "True") %>% 
  
  #code for survey reponse "Are you a recruited athlete?"
  
  mutate(athlete = case_when(q5 == "Yes" ~ 1,
                             q5 == "No" ~ 0,
                             q5 == "N/A" ~ NA_real_)) %>% 
  
  #code for recieved treatment or not, q10 is the intervetion question
  
  mutate(treatment = ifelse(q10 %in% c("Much Easier", "Slightly Easier", "No difference", "Slightly Harder",
                                       "Much Harder"), 1, 0)) %>% 
  mutate(response = case_when(q8 == "Much Easier" ~ -2,
                              q8 == "Slightly Easier" ~ -1,
                              q8 == "No difference" ~ 0,
                              q8 == "Slightly Harder" ~ 1,
                              q8 == "Much Harder" ~ 2)) %>% 
  mutate(response_treated = case_when(q10 == "Much Easier" ~ -2,
                              q10 == "Slightly Easier" ~ -1,
                              q10 == "No difference" ~ 0,
                              q10 == "Slightly Harder" ~ 1,
                              q10 == "Much Harder" ~ 2)) %>% 
  mutate(response_overall = ifelse(response %in% c(-2,-1,0,1,2), response,response_treated))

#save data as csv file for excel 

write_excel_csv(cleaned_survey, "raw_data/cleaned_survey.csv", col_names = TRUE)
```

```{r data exploration}
total_athletes <- cleaned_survey %>% 
  count(athlete)

total_treated <- cleaned_survey %>% 
  count(treatment)

```

## Data

There were 216 total responses. Of those particpants 185 answered they are not a recruited athlete and 20 answered they are a recruited athlete. Particpants were randomly selected to recieve the intervention. Of all 216 participants 109 people were in the control group. They answered this question: "In your opinion, how difficult is it for recruited athletes to be admitted to Harvard compared to other prospective students?". I coded the following answers: (-2) Much easier, (-1) slightly easier, (0) no difference, (1) slightly harder, (2) much harder. 
  

107 people recieved the intervention. They received this blurb before answering the same question above: "Did you know that every recruited student athlete is evaluated through an Academic Index? Harvard’s Academic Index is 220 out of 240 which equates to ~1520 SAT/ 34 ACT and 4.0 GPA. Ivy League rules state that Harvard Athletics must have an average no lower than one standard deviation below 220."



```{r summary stats}
#average answer of control group without athletes

avg_control <- cleaned_survey %>% 
  filter(!is.na(athlete), athlete == 0)  %>% 
  summarise(avg = mean(response, na.rm = TRUE)) %>% 
  pull(avg)

#average answer of treated group

avg_treated <- cleaned_survey %>% 
  filter(!is.na(athlete), athlete == 0) %>% 
  summarise(avg = mean(response_treated, na.rm = TRUE)) %>% 
  pull(avg)

avg_treated - avg_control
#average answer for control just athletes (check sample size, 8)

avg_ath_control <- cleaned_survey %>% 
  filter(!is.na(athlete), athlete == 1) %>% 
  summarise(avg = mean(response, na.rm = TRUE)) %>% 
  pull(avg)

#average answer for treatment just athletes (check sample size, 12)

avg_ath_treated <- cleaned_survey %>% 
  filter(!is.na(athlete), athlete == 1) %>% 
  summarise(avg = mean(response_treated, na.rm = TRUE)) %>% 
  pull(avg)

```

## Results
  
*For data analysis I excluded respondents who indicated they are a recruited athlete*
    
The mean response for the control group is `r avg_control`. This means the control group tended to answer "Slightly Easier". 

The mean response for the treated group is `r avg_treated`. The treated group also tended to answer "Slightly Easier". The difference between the control and treated group is `r avg_treated - avg_control`. This indicates the intervention may have backfired, causing respondents to answer more negatively (towards "Much Easier").

```{r}
#visualize results
graph_data <- cleaned_survey %>% 
  filter(!is.na(athlete), athlete == 0) 

#create labels for graph
treatment.labs <- c("Control", "Treated")
names(treatment.labs) <- c("0", "1")


ggplot(graph_data, aes(response_overall)) + 
  geom_bar() + 
  facet_wrap(~treatment, labeller = labeller(treatment = treatment.labs)) +
  scale_x_continuous(breaks = c(-2,-1,0,1,2), labels = c("Much Easier", "Slightly Easier", "No Difference", "Slightly Harder", "Much Harder")) +
  theme(axis.text.x = element_text(angle = 20)) +
  labs(title = "Distribution of Survey Responses of Non-Athletes",
       caption = "Respondents were asked: In your opinion, when compared to other prospective applicants \n how difficult is it for recruited athletes to be admitted to Harvard?",
       x = "Survey Answer", 
       y = "Answer Count") +
  theme(plot.title = element_text(hjust = .5),
        plot.caption = element_text(hjust = 0))
  
```
```{r bootstrap}

bootstrap_distrib <- cleaned_survey %>%
  rep_sample_n(size = nrow(cleaned_survey), replace = TRUE, reps = 100) %>% 
  group_by(replicate, treatment, athlete) 
  
  #avg bootsrapped control without athletes

#average answer of control group without athletes

avg_bootstrap <- bootstrap_distrib %>% 
  filter(!is.na(athlete), athlete == 0)  %>% 
  summarise(avg = mean(response, na.rm = TRUE)) 


ggplot(avg_bootstrap, aes(avg)) + 
  geom_histogram() +
  facet_wrap(~treatment) +
  geom_vline(xintercept = avg_control)




bootstrap_distrib2 <- cleaned_survey %>% 
  filter(!is.na(athlete), athlete == 0) %>% 
  mutate(treatment_factor = as.factor(treatment)) %>% 
  specify(formula = response_overall ~ treatment_factor) %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 100, type = "permute") %>% 
  calculate(stat = "diff in means", order = c(1, 0))

obs_diff_means <- cleaned_survey %>% 
  filter(!is.na(athlete), athlete == 0) %>% 
  mutate(treatment_factor = as.factor(treatment)) %>% 
  specify(formula = response_overall ~ treatment_factor) %>%
  calculate(stat = "diff in means",  order = c(1,0))

#Ha is that treatment - control > 0 
p_value <- bootstrap_distrib2 %>% 
  get_p_value(obs_stat = obs_diff_means, direction = "right")
```


